Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-09 Ben_Manuscripts/structure_paper/Draft.tex
Minor edits to draft and additions to supplemental information
New and updated figures along with major reworks to figure captions

  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
  %           Thicken slabs
  %           Make pore region on slab (blue) bigger
  %           Bump up atom sizes in atomistic render
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.png}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_blender.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

@@

  % BJC: TODO: Make new rendering of wedges
  %            Change color scheme 
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{Our previous level of understanding of the pore structure (a) only allows us to speculate
	   about transport behavior in the pore. A detailed molecular model (b) will allow us to
	   directly observe solute transport. Here, four stacked layers of 5 NA-GA3C11 monomers
           are pictured from atomistic simulations. The hydrophilic region is in red and the 
	   hydrophobic region is colored blue.}~\label{fig:detail}
  \end{figure}

@@

	\item The location of the first is at $q_z$ = 1.7 \angstrom$^{-1}$,
	corresponding to a real space separation of 3.7 \angstrom~. Previous
	work~\ref{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
	stacking between aromatic rings in the direction perpendicular to the membrane
	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
	this reflection as R-$\pi$.

@@

  %BJC: TODO: update colorbar
  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
%MRS3: would be good to have all feature labels agree: either can edit to put the names on, or have a key relating numbers to the names you use.
%BJC2: I will annotate it with the names R-pi, R-alkanes etc. Is that what you mean?
%MRS4: that works fine.  We just need a way to connect what is in the figure with the names used in the text.  Ideally there would not be two sets of labels, just one.
%BJC3: Got it, will do once I have more time to focus on figures 
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D wide angle X-ray scattering gives
		details about repeating features less than 1 nanometer apart. Experimentalists
		have justified each of the 5 major reflections present as follows: (I) Aromatic
		head group $\pi-\pi$ stack 3.7 \AA~apart.  (II) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (III) Alkane chain tails pack 4.5 \AA~apart. (IV)
		Monomer tails tilt with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  We parameterized the liquid crystal monomers using the Generalized AMBER
  Forcefield \cite{wang_development_2004} with the Antechamber package
  \cite{wang_automatic_2006} provided with AmberTools16
  \cite{case_ambertools16_2016}. We assigned atomic charges using the am1bccsym
  method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
  Software. We ran all molecular dynamics simulations using Gromacs 2016
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  %BJC: TODO: reproduce figure in latex (or gimp?) with higher resolution arrows
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) Python scripts rotate and assemble monomers into layers with 
		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
		pores. (d) The pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems built with 5 monomers per layer in a parallel
		displaced configuration result in a pore spacing closest to the experimental
		value of 4.12 nm. The pore spacing of the model increases as number of monomers
		in each layer increases. The pore spacing of a system starting in the
		sandwiched configuration is systematically slightly lower than that started in
		an offset configuration. }~\label{fig:p2p}
  \end{figure}

@@

  %BJC: TODO: increase font size on legends
  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ number density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

@@

  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.29]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-3.30em}
        \includegraphics[width=\linewidth]{colorbar_jet.png}
  \end{subfigure}
  \caption{The simulated X-ray diffraction patterns for simulations run in the
  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
  The parallel displaced configuration is the only one that exhibits all major
  reflections of interest to some degree}
  \label{fig:XRDsim}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
  indicates an average tilt angle near 7\degree~which is far from the 37\degree~tilt angle 
  previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) We removed all atoms except carbon atoms making up the tails from a 
	sandwiched configuration trajectory. (b) The simulated diffraction pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
        %MRS3: so I didn't realize this before, but why are there still fairly significant peaks in the pi-stacking region when the head groups are removed?
        %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
        %BJC2: Yea, I think the reflection is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
        % in this pattern is lower than in the pattern generated by the full system. The aromatic rings appear to strengthen the reflection. 
        % Also, the system is layered in the z-direction, as we show, so a reflection like that should appear. 
        %MRS4: did you use a different scaling for the color bar here than above? If so, mention.
        %BJC3: The scaling is the same
  \end{figure}

  \begin{figure}[!htb]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure} 
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}[!hbt]
        \centering
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{dbwl.png}
                \caption{}~\label{fig:dbwl_disordered}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{p2p2.png}
                \caption{}~\label{fig:p2p_disordered}
        \end{subfigure}
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
                \caption{}~\label{fig:offset_disordered_xrd}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
                \caption{}~\label{fig:layered_disordered_xrd}
        \end{subfigure}
	\caption{In comparison to the ordered pore systems, the simulated
		X-ray diffraction patterns of the parallel displaced (a) and sandwiched (b)
		configurations are different than the disordered pore systems , most notably in
		the region bounded by R-alkanes.  When layers are initially stacked further
		apart, the distance between layers increases (c) and the pore spacing decreases
		(d).}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel displaced, 3.7 \AA~initial layer spacing}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, 3.7 \AA~initial layer spacing}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel displaced, 5 \AA~initial layer spacing}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, 5 \AA~initial layer spacing}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.  }~\label{fig:densities}
  \end{figure}

>>>>

  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
  %           Thicken slabs
  %           Make pore region on slab (blue) bigger
  %           Bump up atom sizes in atomistic render
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

@@

  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{We can only speculate about solute behavior inside the membrane
	  pores based on our previous picture of the pore structure (a). We will use a
	  detailed molecular model in order to appropriately model the pore's complex
	  architecture which is crucial to understanding the mechanism of solute
	  transport (b). The head group region is colored blue
	  and the tail region is colored cyan in both representations.}~\label{fig:detail}
  \end{figure}

@@

	\item The location of the first is at $q_z$ = 1.7 \angstrom$^{-1}$,
	corresponding to a real space separation of 3.7 \angstrom~. Previous
	work~\cite{feng_scalable_2014} attributes this reflection to $\pi$-$\pi$
	stacking between aromatic rings in the direction perpendicular to the membrane
	plane, or z-axis \cite{feng_scalable_2014}. For simplicity, we will refer to
	this reflection as R-$\pi$.

@@

  %BJC: TODO: update colorbar
  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
%BJC: What do you think of the labels now? I tried to make it more clear what each label refers
% to graphically. I can't decide if it's too cluttered. An alternative is to number them as  
% I had them before, and then define them in a little box inset to the figure
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-helix) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  We parameterized the liquid crystal monomers using the Generalized AMBER
  Force Field \cite{wang_development_2004} with the Antechamber package
  \cite{wang_automatic_2006} provided with AmberTools16
  \cite{case_ambertools16_2016}. We assigned atomic charges using the am1bccsym
  method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
  Software. We ran all molecular dynamics simulations using Gromacs 2016
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  %BJC: TODO: reproduce figure in latex (or gimp?) with higher resolution arrows
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) A python script rotates and assembles monomers into layers with 
		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
		pores. (d) The pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{When we build systems with 5 monomers per layer in the
		parallel displaced configuration, the equilibrated pore spacing is closest to
		the experimental value of 4.12 nm. The equilibrated pore spacing of the model
		increases as the number of monomers in each layer increases. The pore spacing
		of systems starting in the sandwiched configuration is systematically slightly
		lower than those started in the parallel displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  %BJC: TODO: increase font size on legends
  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
	\caption{We support the existence of layers with the observance of
		clear periodic maxima in the $z$-direction pair distribution functions of the
		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
		displaced configurations. The extent to which we consider a system to be
		layered is based on the magnitude of the deviation of the periodic maxima from
		the average number density. The sandwiched configuration possesses a higher
		degree of layering than the parallel displaced configuration and, in both
		cases, the head group region has a higher degree of layer partitioning than the
		tail region. (See supplemental information for detailed definitions of the head
		group and tail regions)}\label{fig:zdf}
  \end{figure}

@@

  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.018\linewidth]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.29]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-4.00em}
        \includegraphics[width=\linewidth]{colorbar_jet.png}
  \end{subfigure}
  \caption{The simulated XRD pattern generated from the equilibrated trajectory
	  of the parallel displaced configuration (a) exhibits all major reflections
	  present in the experimental WAXS pattern (b). The simulated XRD pattern
	  generated from the equilibrated trajectory in the sandwiched configuration shows
	  all major reflections except R-helix.}
  \label{fig:XRDsim}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the membrane plane. 
  The average tilt angle is near 7\degree~which is far from the 37\degree~tilt angle 
  previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
	 	\vspace{-2em}
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
        %MRS3: so I didn't realize this before, but why are there still fairly significant peaks in the pi-stacking region when the head groups are removed?
        %Do you feel you understand this? I suppose it is because the top of the tails must be correlated with the aromatic ring by covalent bonding?
        %BJC2: Yea, I think the reflection is correlated to the aromatic rings. The system shown is the sandwiched configuration. The intensity of "R-pi"
        % in this pattern is lower than in the pattern generated by the full system. The aromatic rings appear to strengthen the reflection. 
        % Also, the system is layered in the z-direction, as we show, so a reflection like that should appear. 
        %MRS4: did you use a different scaling for the color bar here than above? If so, mention.
        %BJC3: The scaling is the same
  \end{figure}

  \begin{figure}[!htb]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure} 
  \caption{We hypothesize that R-spots is the result of ordered tail packing.
	  Defining the membrane plane to be 0\degree, we
	  measured the angles between each alkane chain tail centroid and its nearest
	  neighbor centroids for the equilibrated parallel displaced (a) and sandwiched
	  (c) configurations. Peaks that appear in each distribution are centered near
	  $\pm~33\degree$. We radially integrated the simulated XRD patterns of the
	  parallel displaced and sandwiched configuration within the region bounding
	  R-alkanes ((b) and (d) respectively).  Peaks appear in the same location as the
	  angle distributions which corroborates our hypothesis. Further, we note that
	  the peaks are strongest in both plots associated with the sandwiched
	  configuration. As shown in Figure \ref{fig:rz_layered}, systems simulated in
	  the sandwiched configuration exhibit more intense R-spots
	  reflections.}~\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}[!hbt]
        \centering
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{dbwl.png}
                \caption{}~\label{fig:dbwl_disordered}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{p2p2.png}
                \caption{}~\label{fig:p2p_disordered}
        \end{subfigure}
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
                \caption{}~\label{fig:offset_disordered_xrd}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
                \caption{}~\label{fig:layered_disordered_xrd}
        \end{subfigure}
	\caption{There are distinct differences between the disordered and ordered pore systems. 
		When layers are initially stacked 5\AA~ apart, the distance
		between layers increases (a) and the pore spacing decreases (b) in comparison to
		the ordered pore systems. The simulated
		XRD patterns of disordered pore systems are also appreciably different, most 
		notably in the region bounded by R-alkanes. The disordered pore
		systems started in the parallel displaced configuariton (c) does not show R-spots
		or R-$\pi$ which suggests that head groups are not associating with each other
		and tails are distributed nearly isotropically. The disordered pore system
		started in the sandwiched configuration (d) does not show R-$\pi$ but R-spots 
		is present in different locations because the tails are packed in a different
		motif.}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel displaced, 3.7 \AA~initial layer spacing}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, 3.7 \AA~initial layer spacing}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel displaced, 5 \AA~initial layer spacing}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, 5 \AA~initial layer spacing}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}
